%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {PhD Student - CONICET} % Job title
    {Mycology Research and Development Laboratory (LIDeMi); (IMPAM, CONICET - UBA)} % Organisation
    {Buenos Aires, Argentina.} % Location
    {Apr 2017 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Molecular identification of fungal cryptospecies.}%
        \item {Anti-fungal susceptibility studies based on international standardized guidelines (CLSI \& EUCAST).}%
        \item {Molecular characterization of azole's resistance mechanisms in \textit{Aspergillus spp}.}%
        \item {Build-up and curation of clinical fungal strains database.}%
        \item {Phylogeny of filamentous fungi.}%
        \item {Studies on Antarctic animals' fungal flora.}%
        \item {Development of polymeric micelles capable of storing and sustainably releasing voriconazole in the lung.}%
        \item {\textbf{Technical skills:} PCR, sequencing, bio-informatics, phylogeny, molecular biology techniques, microbiology, data analysis, micro y nano particles formulation.}%
        \item {\textbf{Soft Skills:} Teamwork, communication skills, written and oral results' presentation, project management, organization of the work environment, planning, people training.}%
      \end{cvitems}%
    }

 \cventry
    {ESV scholarship} % Job title
    {Biological Interactions Research Laboratory (LIIB); Universidad Nacional De Quilmes} % Organisation
    {Buenos Aires, Argentina.} % Location
    {Sep 2013 - Aug 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Study of the native actinorrhizal symbiosis that establishes nitrogen-fixing root nodules between \textit{Frankia spp.} and \textit{Discaria trinervis'} roots.}
        \item{Genetic transformation of roots by \textit{A. rhizogenes.}}
        \item {\textbf{Technical skills:} Molecular biology techniques, microbiology,  fluorescence microscopy, data analysis.}
        \item {\textbf{Soft Skills:} Teamwork, communication skills, written and oral results' presentation.}
      \end{cvitems}
    }
\end{cventries}

