%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
%  \cventry
%    {Instituto De Investigaciones En Microbiología Y Parasitología Médica (IMPAM)} % Organisation
%    {} % Project
%    {} % Location
%    {} % Date(s)
%    {
%      \begin{cvitems} % Description(s) of project
%        \item {}
%        \item {}
%        \item {\textbf{Capacidades técnicas:} R with ggplot2, tidyr, R Markdown.}
%        \item {\textbf{Soft Skills:} Report writing, Logical Thinking, Critical Thinking.}
%      \end{cvitems}
%    }
%---------------------------------------------------------
  \cventry
    {Dirección Nacional del Antártico (DNA) - Instituto Antártico Argentino (IAA)} % Organisation
    {Studies on the diversity of fungal species from clinical samples of animals of the Antarctic fauna: potential impact on human health} % Project
    {Carlini station,\newline Antártida Argantina} % Location
    {Jan 2019 - Mar 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {The aim was to contribute to the knowledge of the epidemiology of yeast-like and filamentous fungi isolated from different biological samples of Antarctic animals. Isolates were characterized by genomic sequencing.}
        \item {\textbf{Technical skills:} PCR, sequencing, bioinformatics, data analysis.}
        \item {\textbf{Soft Skills:} Teamwork, critical thinking, project organization and management, planning, development of written reports.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Instituto De Investigaciones En Microbiología Y Parasitología Médica (IMPAM)} % Organisation
    {Implementation and maintenance of the institute's website} % Project
    {Buenos Aires, AR} % Location
    {Jun 2019 - Current} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Design and maintenance of the institute's website. Data collection using Google Forms and development of the institute's staff database.}
        \item {\textbf{Technical skills:} Google Forms, Google Docs, HTML, WordPress.}
        \item {\textbf{Soft Skills:} Teamwork, critical thinking, project organization and management.}
      \end{cvitems}
    }
%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\vspace{15mm}
\cvsection{Talks and Conferences}
%\vspace{1mm}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Newland's Highschool} % Institución
    {Antarctica, Fungi and Humans: A one world-one health concept} % Nombre
    {Bs.As., AR} % Location
    {Nov 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Talk for secondary school students organized by Newland's Highschool as part of the awareness week "Taking Care of Me to Take Care of You". The objective was to bring students closer to the world of research and inform them of key concepts such as "One World - One Health", Ecosystems and Mycology.
. }
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Veterinary school - University of Buenos Aires} % Institución
    {Aspergilossis - Overview and Diagnosis} % Nombre
    {Bs.As., AR} % Location
    {Oct 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Invited lecturer at a seminar for postgraduate students.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Veterinary school - University of Buenos Aires} % Institución
    {Antifungals - Mechanisms and Resistances} % Nombre
    {Bs.As., AR} % Location
    {Oct 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of project
        \item {Invited lecturer at a seminar for postgraduate students.}
      \end{cvitems}
    }
%---------------------------------------------------------

\end{cventries}
